\documentclass{letter}
\usepackage[margin=1in]{geometry}

\address{800 Dongchuan Rd., Shanghai}
\signature{Yihao Liu}

\begin{document}

First Draft:

My name is Yihao Liu, a senior student in ECE. My interest of further study is in systems track, including distributed systems and operating systems. After my graduation, I'll continue my master or PhD study and do some research in this area id I would have an opportunity for it.

\bigskip

Revised Draft: (on the next page)

\begin{letter}{}

\opening{Dear Dr. Murray,}

My name is Yihao Liu, a senior student in University of Michigan - Shanghai Jiao Tong University Joint Institute majored in ECE (Electrical and Computer Engineering). I also took a minor in Data Science and a second degree in Applied Mathematics. I'm particularly interested in the System area under Computer Science. I am highly motivated in conducting research in Operating Systems and Distributed Systems in the future.

After my graduation, I would like to pursue graduate study in a university in the United States of America. The master and PhD programs there aims at training future scientists who can make critical observations and tackle the most challenging problems, which is also my academic goals. I am ready to move up to the next level and contribute to the community.

I would like to develop my skills in academic writing and presentations in this course, which are  widely used among researchers for publications and conferences. The academic writing courses (VY100 and VY200) in the institute don't cover much on formality and specifications on technical writing, so I will be appreciated if these could be included in your course.

\closing{Yours respectfully,}

\end{letter}

\end{document}
 
